\documentclass[options]{article}
\begin{document}

{\textbf{PREPARATION FOR WORK.}}


{PREPARED BY: MABINGO JOSHUA, 15/U/7254/EVE, 215011664.}

\section{\textbf{Introduction}}
I most of the times wakeup at 6:00 am every day and kick start my daily routine as follows:

\section{\textbf{Preparation for a shower.}}
When I get out of bed, I then get hold of my towel, tooth brush, soap and tooth paste and the slowly I walk to the shower room.

\subsection{\textbf{Bathing. }}
On my getting I to the bathroom, I remove my clothes ad open the shower after putting soap In my sponge, scrubbing my body well until there feels no soap at all on my body. I then wipe my body well and dress up again.

\subsection{\textbf{Brushing}}
After showering, I then put tooth paste on my brush and move to the sink, I the open the tap ad brush my teeth thoroughly, my tongue and the rise the mouth so well. I then clean my brush and the move back to my room.

\subsection{\textbf{Preparing what to put on }}
Out of my wardrobe, I pick my shoes and the clothes to put on that day.  

\subsection{\textbf{Polishing my shoes }}
 I then pick out the shoe brush and the shoe polish I polish my shoes and wipe them clean to make them shine.

\subsection{\textbf{Ironing my clothes }} 
I then pull out the flat iron ad I the iron my clothes.

\subsection{\textbf{Dressing up}}
Then finally after all that, I dress up my attires and get hold of my bag.

\subsection{\textbf{Praying}}
I then place the day into God’s hands and off I go to work.


\end{document}